\documentclass[10pt,a4paper,ragged2e,withhyper]{altacv}
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}
\usepackage{paracol}

\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{DarkPastelRed}{HTML}{450808}
\definecolor{PastelRed}{HTML}{8F0D0D}
\definecolor{GoldenEarth}{HTML}{E7D192}
\colorlet{name}{black}
\colorlet{tagline}{PastelRed}
\colorlet{heading}{DarkPastelRed}
\colorlet{headingrule}{GoldenEarth}
\colorlet{subheading}{PastelRed}
\colorlet{accent}{PastelRed}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

\renewcommand{\namefont}{\Huge\rmfamily\bfseries}
\renewcommand{\personalinfofont}{\footnotesize}
\renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
\renewcommand{\cvsubsectionfont}{\large\bfseries}
\renewcommand{\cvItemMarker}{{\small\textbullet}}
\renewcommand{\cvRatingMarker}{\faCircle}

\begin{document}

\name{Emil Zaripov}
\tagline{Product Manager • EdTech Strategist • B2G Lead}
\personalinfo{
  \email{emil@emilka.ru}
  \phone{+7 926 986 20 17}
  \location{Moscow, Russia}
}

\makecvheader

\columnratio{0.6}
\begin{paracol}{2}

\cvsection{Experience}

\cvevent{Founder / CPO, Digital Products}{Ooly Group}{Sep 2020 -- Present}{Moscow, Russia}
\begin{itemize}
  \item Built and scaled tech products across EdTech, PropTech, GovTech, and IoT.
  \item Delivered full-cycle B2G/B2B solutions: discovery, development, implementation, scaling.
  \item Led digital projects for top real estate developers (PIK, LSR) and public clients (Moscow Department of Health, IT, and Culture).
\end{itemize}

\divider

\cvevent{Initiatives Lead (Student Government)}{Higher School of Economics (HSE)}{Sep 2023 -- Apr 2024}{Moscow, Russia}
\begin{itemize}
  \item Acted as a key decision-maker in HSE's student governance system—one of the largest of its kind globally, involving 500+ active members.
  \item Supervised the university’s crisis response center during a national emergency; coordinated communication with first-level leadership.
  \item Launched digital products and services used by 60,000+ students across HSE campuses.
  \item Developed and implemented custom solutions for internal elections and student governance.
  \item Led technical coordination with central administration and faculty heads.
\end{itemize}

\cvsection{Projects}

\cvevent{Corporate Learning Platform for EMS}{Medical Education • B2G}{2020 -- Present}{}
\begin{itemize}
  \item Created Russia’s first full-cycle corporate university in a public medical institution.
  \item 50,000+ total users, ~5,000 daily; integrated with federal systems
  \item Enabled onboarding-to-upskilling journey, agility in workforce planning, and higher engagement.
\end{itemize}

\divider

\cvevent{CloudLink}{Access Control • B2G}{2021 -- Present}{}
\begin{itemize}
  \item Developed PACS solution for 130+ Moscow schools.
  \item Integrated with the federal Moskvyonok system; enhanced safety and data access.
\end{itemize}

\divider

\cvevent{RinGate}{Smart Home IoT • PropTech}{2024 -- Present}{}
\begin{itemize}
  \item Partnered with Domyland (Top-1 PropTech company in Russia) and major developers.
  \item Delivered access, surveillance, and automation infrastructure from builder's perspective.
\end{itemize}

\divider

\cvevent{Hostronaut}{Web Hosting}{2019 -- 2020}{}
\begin{itemize}
  \item Grew to 10,000+ users in one year with \$0 ad budget.
  \item Monetized via affiliate model; later acquired by TimeWeb.
\end{itemize}

\cvsection{Education}

\cvevent{BSc Applied Math and Computer Science}{Higher School of Economics (HSE)}{2024 -- Expected 2028}{Moscow, Russia}

\switchcolumn

\cvsection{Achievements}

\cvachievement{\faBookMedical}{Pioneered Public Sector EdTech}{Built the first full-cycle corporate university in healthcare in Russia.}

\cvachievement{\faUsers}{Large-Scale Product Delivery}{Designed and launched systems for 50,000–60,000+ users in gov and education.}

\cvachievement{\faCogs}{Cross-Sector Experience}{Brought innovation to EdTech, urban infrastructure, healthcare, and IoT.}

\cvsection{Proud Of}

\cvachievement{\faLayerGroup}{Coordinating 10–100 Person Teams}{Led cross-functional groups across education, product, and implementation tracks.}

\cvachievement{\faLightbulb}{Creating from Scratch}{Conceptualized and delivered products in uncharted spaces with no analogues.}

\cvsection{Skills}

\cvtag{Product Strategy}
\cvtag{Cross-functional Leadership}
\cvtag{EdTech / GovTech}
\cvtag{B2G Partnerships}
\cvtag{UX Research \& Prototyping}
\cvtag{SQL / Python / Git}
\cvtag{Agile / Scrum / Kanban}
\cvtag{Market Discovery}

\cvsection{Languages}

\cvskill{Russian (Native)}{5}
\divider
\cvskill{English (Fluent, C1)}{4.5}
\divider
\cvskill{French (Basic)}{2}

\cvsection{References}
\cvref{Available upon request}{}{emil@emilka.ru}

\end{paracol}
\end{document}
\textbf{}
